Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-01-28 paper/paper.tex
updated ACM style

\documentclass[sigconf,screen,anonymous]{acmart}

@@

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}

@@

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{1997}
\copyrightyear{2016}

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). This paper evaluates the potential
benefits of diversity techniques, including DT. It provides data to
support or not the decision for automation of these techniques.

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}. Our results indicate that both
techniques were successful at finding bugs, but, overall, test
transplantation demanded less effort compared to differential testing
per bug found. Although our experience indicates that more research
needs be done to automate parts of the inspection process, our results
show that exploring diversity is a valuable help to find bugs in
JavaScript engines.

\emph{Key Findings.}~\Fix{copied from ICSE meta-review $\rightarrow$}The key
findings could include, e.g.: - Not only multiple different
implementations can be leveraged in differential testing, also
differences in test suites can be important.  - Even for problems with
fairly clear specifications, as here for a programming language and
how it is to be executed, there is likely to be (a lot of) variation
between different implementations.  - Differential testing is feasible
on real, complex, widely used pieces of software.

@@

The specification and implementation of JavaScript are
incomplete. Certain parts of the specification are undefined; it is
responsibility of engine engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration
order of elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for optimization~\cite{for-in-undefined}.  As another
example, the specification states that if
the \mcodeid{Number.toPrecision()} function is called with multiple arguments then the floating-point approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Such gap also exists at the
implementation level. Given the speed the specification changes and
the complexity of the language some features are not fully implemented
as can be observed by the Kangax compatibility table~\cite{kangax}.
It is also worth noting that, as in other languages, some
elements in JS have non-deterministic behavior (\eg{},
\mcodeid{Math.random} and \mcodeid{Date}). A test that make decisions
based on these elements could, in principle, produce different
outcomes on different runs. Carefully-written test cases should not
manifest this kind of
flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
fuzzed are more likely to manifest them.
As mentioned previously, all those aspects make testing \js\ engines
more challenging.

@@

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t!]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}

@@

%The checker can produce multiple warnings for a given input.

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the conformance of the engines we studied
using the official Test262 conformance
suite~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that developers
consider different goals when writing test cases--suites written for a
given engine should cover scenarios not covered by a different
engine. Third, we analyzed the impact of using cross-engine
differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
is that bugs may be detected using inputs which are similar to those
already tested. Our broad goal is to evaluate ability of these simple
diversity-aware techniques in bug finding.

%Figure~\ref{fig:summary} summarizes the bugs we reported.

@@

\subsection{Conformance}
\label{sec:stability}

@@

\subsection{Test Transplantation}
\label{sec:transplantation}

@@

\subsection{Cross-Engine Differential Testing}
\label{sec:cross-engine-diff-testing-results}

This section reports the results obtained with differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. Considering \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

>>>>

\documentclass[sigconf,review, anonymous]{acmart}

@@

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}

@@

%Conference
\acmConference[ESEC/FSE 2019]{The 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{26--30 August, 2019}{Tallinn, Estonia}
\acmYear{1997}
\copyrightyear{2016}

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). \Mar{rewrite. too vague.}\Fix{This paper
  evaluates the potential benefits of diversity techniques, including
  DT. It provides data to support or not the decision for automation
  of these techniques.}

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}.

\emph{Key Findings.}~Results indicate that both techniques were
successful at finding bugs. Overall, test transplantation demanded
less effort compared to differential testing per bug
found.\Fix{redundant with the sentences that follow...check} Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript
engines. \Fix{copied from ICSE meta-review $\rightarrow$}The key
findings could include, e.g.: - Not only multiple different
implementations can be leveraged in differential testing, also
differences in test suites can be important.  - Even for problems with
fairly clear specifications, as here for a programming language and
how it is to be executed, there is likely to be (a lot of) variation
between different implementations.  - Differential testing is feasible
on real, complex, widely used pieces of software.

@@

For different reasons, the specification and implementation of
JavaScript are incomplete. Certain parts of the specification are
undefined; it is responsibility of engineers to decide how to
implement these functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for optimization~\cite{for-in-undefined}.
As another example, the specification states that if the
\mcodeid{Number.toPrecision()} function is called with multiple
arguments then the floating-point approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Such gap also exists at the
implementation level. Given the speed the specification changes and
the complexity of the language some features are not fully implemented
as can be observed by the Kangax compatibility table~\cite{kangax}.
It is also worth noting that, as in other languages, some elements in
JS have non-deterministic behavior (\eg{}, \mcodeid{Math.random} and
\mcodeid{Date}). A test that make decisions based on these elements
could, in principle, produce different outcomes on different
runs. Carefully-written test cases should not manifest this kind of
flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}.  As
mentioned previously, all those aspects make testing \js\ engines more
challenging.

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging on diversity of test data and engine implementations. Based
on that, we pose three questions:
\begin{description}[leftmargin=.5in]
\item[RQ1.] How conformant are the engines to the Test262 suite?
\item[RQ2.] How effective is test transplantation to find bugs?
\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
\end{description}

The first question focuses on the conformance of our selected engines
to the official Test262 suite~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. The second question
focuses on the effectiveness of test transplantation
(Section~\ref{sec:transplantation}). The rationale for using inputs
from different engines is that developers consider different goals
when writing test cases--suites written for a given engine should
cover scenarios not covered by a different engine. The third question
evaluates the effectiveness of cross-engine differential testing to
find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that bugs may be detected using inputs which are similar
to those already tested. Overall, our goal is to evaluate ability of
these simple diversity-aware techniques to find bugs.

@@

\subsection{Answering RQ1 (Conformance)}
\label{sec:stability}

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~...
      \end{minipage}
    }
\end{center}

\subsection{Answering RQ2 (Test Transplantation)}
\label{sec:transplantation}

@@

\subsection{Answering RQ3 (Differential Testing)}
\label{sec:cross-engine-diff-testing-results}

This section reports the results obtained with cross-engine differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. Considering \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.
